### 2023-09-28 proofs/main.tex
Fix file dirs

\input{../_build/_gen/included.tex}

@@

\subsection{Type Well-formedness}
\input{../_build/_gen/tex/wf-lemmas.tex}

\subsection{Substitution}
\input{../_build/_gen/tex/subst-lemmas.tex}

\subsection{Declarative Subtyping}
\input{../_build/_gen/tex/decl-subtyping-lemmas.tex}

\subsection{Equivalence}
\label{sec:decl-equiv-lemmas}
\input{../_build/_gen/tex/equiv-lemmas.tex}

\subsection{Variable Ordering}
\input{../_build/_gen/tex/ord-lemmas.tex}

\subsection{Normaliztaion}
\input{../_build/_gen/tex/norm-lemmas.tex}

@@

\subsection{Algorithmic Type Well-formedness}
\input{../_build/_gen/tex/wf-algo-lemmas.tex}

\subsection{Substitution}
\input{../_build/_gen/tex/subst-algo-lemmas.tex}

\subsection{Normalization}
\input{../_build/_gen/tex/norm-alg-lemmas.tex}

\subsection{Equivalence}
\input{../_build/_gen/tex/equiv-alg-lemmas.tex}

\subsection{Unification Constraint Merge}
\input{../_build/_gen/tex/unif-constraint-merge-lemmas.tex}

\subsection{Unification}
\input{../_build/_gen/tex/unification-lemmas.tex}\

\subsection{Anti-unification}
\input{../_build/_gen/tex/au-lemmas.tex}

\subsection{Upper Bounds}
\label{sec:alg-upper-bounds-proofs}
\input{../_build/_gen/tex/lub-lemmas.tex}

\subsection{Upgrade}
\label{sec:upgrade-lemmas}
\input{../_build/_gen/tex/upgrade-lemmas.tex}

\subsection{Constraint Satisfaction}
\input{../_build/_gen/tex/constraint-sat-lemmas.tex}

\subsection{Positive Subtyping}
\input{../_build/_gen/tex/alg-pos-subtyping-lemmas.tex}

\subsection{Subtyping Constraint Merge}
\input{../_build/_gen/tex/constraint-merge-lemmas.tex}

\subsection{Negative Subtyping}
\input{../_build/_gen/tex/alg-neg-subtyping-lemmas.tex}

\section{Properties of the Declarative Typing}
\input{../_build/_gen/tex/decl-typing-lemmas.tex}

@@

\subsection{Singularity}
\input{../_build/_gen/tex/singularity-lemmas.tex}

\subsection{Correctness of the Typing Algorithm}
\input{../_build/_gen/tex/alg-typing-lemmas.tex}

>>>>

\newcommand{\ottDir}{../ott/_gen}
\newcommand{\genDir}{_gen}
\input{\ottDir/included.tex}

@@

\subsection{Type Well-formedness}
\input{\genDir/tex/wf-lemmas.tex}

\subsection{Substitution}
\input{\genDir/tex/subst-lemmas.tex}

\subsection{Declarative Subtyping}
\input{\genDir/tex/decl-subtyping-lemmas.tex}

\subsection{Equivalence}
\label{sec:decl-equiv-lemmas}
\input{\genDir/tex/equiv-lemmas.tex}

\subsection{Variable Ordering}
\input{\genDir/tex/ord-lemmas.tex}

\subsection{Normaliztaion}
\input{\genDir/tex/norm-lemmas.tex}

@@

\subsection{Algorithmic Type Well-formedness}
\input{\genDir/tex/wf-algo-lemmas.tex}

\subsection{Substitution}
\input{\genDir/tex/subst-algo-lemmas.tex}

\subsection{Normalization}
\input{\genDir/tex/norm-alg-lemmas.tex}

\subsection{Equivalence}
\input{\genDir/tex/equiv-alg-lemmas.tex}

\subsection{Unification Constraint Merge}
\input{\genDir/tex/unif-constraint-merge-lemmas.tex}

\subsection{Unification}
\input{\genDir/tex/unification-lemmas.tex}\

\subsection{Anti-unification}
\input{\genDir/tex/au-lemmas.tex}

\subsection{Upper Bounds}
\label{sec:alg-upper-bounds-proofs}
\input{\genDir/tex/lub-lemmas.tex}

\subsection{Upgrade}
\label{sec:upgrade-lemmas}
\input{\genDir/tex/upgrade-lemmas.tex}

\subsection{Constraint Satisfaction}
\input{\genDir/tex/constraint-sat-lemmas.tex}

\subsection{Positive Subtyping}
\input{\genDir/tex/alg-pos-subtyping-lemmas.tex}

\subsection{Subtyping Constraint Merge}
\input{\genDir/tex/constraint-merge-lemmas.tex}

\subsection{Negative Subtyping}
\input{\genDir/tex/alg-neg-subtyping-lemmas.tex}

\section{Properties of the Declarative Typing}
\input{\genDir/tex/decl-typing-lemmas.tex}

@@

\subsection{Singularity}
\input{\genDir/tex/singularity-lemmas.tex}

\subsection{Correctness of the Typing Algorithm}
\input{\genDir/tex/alg-typing-lemmas.tex}
